\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-19 papers/jss/article.Rnw
Remove tables 3-8 with full slot and method descriptions for each class in RProtoBuf.  This belongs in the documentation, not the paper. Refer the reader to the full docs once at the beginning of this section and remove all the references to tables in each subsection. Further minor edits are needed here.  This was suggested by referee #1.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@901 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Table~\ref{class-summary-table} lists the six primary Message and
Descriptor classes in \pkg{RProtoBuf}.
% Please see the package
%documentation for a complete description of the slots and methods for
%each class.

\begin{table}[bp]
\centering
\begin{tabular}{lccl}
\toprule
Class               & Slots & Methods & Dynamic dispatch\\
\cmidrule{2-4}
Message             & 2 & 20 & yes (field names)\\
Descriptor          & 2 & 16 & yes (field names, enum types, nested types)\\
FieldDescriptor     & 4 & 18 & no\\
EnumDescriptor      & 4 & 11 & yes (enum constant names)\\
EnumValueDescriptor & 3 & \phantom{1}6 & no\\
FileDescriptor      & 3 & \phantom{1}6 & yes (message/field definitions)\\
\bottomrule
\end{tabular}
\caption{\label{class-summary-table}Overview of class, slot, method and
  dispatch relationships.}
\end{table}

@@

The \code{Message} S4 class represents Protocol Buffer Messages and
is the core abstraction of \pkg{RProtoBuf}. Each \code{Message}
contains a pointer to a \code{Descriptor} which defines the schema
of the data defined in the Message, as well as a number of
\code{FieldDescriptors} for the individual fields of the message.  A
complete list of the slots and methods for \code{Messages}
is available in Table~\ref{Message-methods-table}.

@@

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & External pointer to the \code{Message} object of the \proglang{C++} protobuf library. Documentation for the
\code{Message} class is available from the Protocol Buffer project page. \\
%(\url{http://code.google.com/apis/protocolbuffers/docs/reference/cpp/google.protobuf.message.html#Message}) \\
\code{type} & Fully qualified name of the message. For example a \code{Person} message
has its \code{type} slot set to \code{tutorial.Person} \\[.3cm]

Method & Description \\
\cmidrule(r){2-2}
\code{has} & Indicates if a message has a given field.   \\
\code{clone} & Creates a clone of the message \\
\code{isInitialized} & Indicates if a message has all its required fields set\\
\code{serialize} & serialize a message to a file, binary connection, or raw vector\\
\code{clear} & Clear one or several fields of a message, or the entire message\\
\code{size} & The number of elements in a message field\\
\code{bytesize} & The number of bytes the message would take once serialized\\[3mm]
%
\code{swap} & swap elements of a repeated field of a message\\
\code{set} & set elements of a repeated field\\
\code{fetch} & fetch elements of a repeated field\\
\code{setExtension} & set an extension of a message\\
\code{getExtension} & get the value of an extension of a message\\
\code{add} & add elements to a repeated field \\[3mm]
%
\code{str} & the \proglang{R} structure of the message\\
\code{as.character} & character representation of a message\\
\code{toString} & character representation of a message (same as \code{as.character}) \\
\code{as.list} & converts message to a named \proglang{R} list\\
\code{update} & updates several fields of a message at once\\
\code{descriptor} & get the descriptor of the message type of this message\\
\code{fileDescriptor} & get the file descriptor of this message's descriptor\\
\hline
\end{tabular}
\end{small}
\caption{\label{Message-methods-table}Description of slots and methods for the \code{Message} S4 class.}
\end{table}

@@

Table~\ref{Descriptor-methods-table} provides a complete list of the
slots and available methods for Descriptors.

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & External pointer to the \code{Descriptor} object of the \proglang{C++} proto library. Documentation for the
\code{Descriptor} class is available from the Protocol Buffer project page.\\
%\url{http://code.google.com/apis/protocolbuffers/docs/reference/cpp/google.protobuf.descriptor.html#Descriptor} \\
\code{type} & Fully qualified path of the message type. \\[.3cm]
%

Method & Description \\
\cmidrule(r){2-2}
\code{new} & Creates a prototype of a message described by this descriptor.\\
\code{read} & Reads a message from a file or binary connection.\\
\code{readASCII} & Read a message in ASCII format from a file or
text connection.\\
\code{name} & Retrieve the name of the message type associated with
this descriptor.\\
\code{as.character} & character representation of a descriptor\\
\code{toString} & character representation of a descriptor (same as \code{as.character}) \\
\code{as.list} & return a named
list of the field, enum, and nested descriptors included in this descriptor.\\
\code{asMessage} & return DescriptorProto message. \\
\code{fileDescriptor} & Retrieve the file descriptor of this
descriptor.\\
\code{containing\_type} & Retrieve the descriptor describing the message type containing this descriptor.\\
\code{field\_count} & Return the number of fields in this descriptor.\\
\code{field} & Return the descriptor for the specified field in this descriptor.\\
\code{nested\_type\_count} & The number of nested types in this descriptor.\\
\code{nested\_type} & Return the descriptor for the specified nested 
type in this descriptor.\\
\code{enum\_type\_count} & The number of enum types in this descriptor.\\
\code{enum\_type} & Return the descriptor for the specified enum
type in this descriptor.\\
\bottomrule
\end{tabular}
\end{small}
\caption{\label{Descriptor-methods-table}Description of slots and methods for the \code{Descriptor} S4 class.}
\end{table}

@@

The class \emph{FieldDescriptor} represents field
descriptors in \proglang{R}. This is a wrapper S4 class around the
\code{google::protobuf::FieldDescriptor} \proglang{C++} class.
Table~\ref{fielddescriptor-methods-table} describes the methods
defined for the \code{FieldDescriptor} class.

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & External pointer to the \code{FieldDescriptor} \proglang{C++} variable \\
\code{name} & Simple name of the field \\
\code{full\_name} & Fully qualified name of the field \\
\code{type} & Name of the message type where the field is declared \\[.3cm]
%

Method & Description \\
\cmidrule(r){2-2}
\code{as.character} & Character representation of a descriptor\\
\code{toString} & Character representation of a descriptor (same as \code{as.character}) \\
\code{asMessage} & Return FieldDescriptorProto message. \\
\code{name} & Return the name of the field descriptor.\\
\code{fileDescriptor} & Return the fileDescriptor where this field is defined.\\
\code{containing\_type} & Return the containing descriptor of this field.\\
\code{is\_extension} & Return TRUE if this field is an extension.\\
\code{number} & Gets the declared tag number of the field.\\
\code{type} & Gets the type of the field.\\
\code{cpp\_type} & Gets the \proglang{C++} type of the field.\\
\code{label} & Gets the label of a field (optional, required, or repeated).\\
\code{is\_repeated} & Return TRUE if this field is repeated.\\
\code{is\_required} & Return TRUE if this field is required.\\
\code{is\_optional} & Return TRUE if this field is optional.\\
\code{has\_default\_value} & Return TRUE if this field has a default value.\\
\code{default\_value} & Return the default value.\\
\code{message\_type} & Return the message type if this is a message type field.\\
\code{enum\_type} & Return the enum type if this is an enum type field.\\
\bottomrule
\end{tabular}
\end{small}
\caption{\label{fielddescriptor-methods-table}Description of slots and
  methods for the \code{FieldDescriptor} S4 class.}
\end{table}

@@

The class \emph{EnumDescriptor} represents enum descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::EnumDescriptor} \proglang{C++} class.
Table~\ref{enumdescriptor-methods-table} describes the methods
defined for the \code{EnumDescriptor} class.

@@

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & External pointer to the \code{EnumDescriptor} \proglang{C++} variable \\
\code{name} & Simple name of the enum \\
\code{full\_name} & Fully qualified name of the enum \\
\code{type} & Name of the message type where the enum is declared \\[.3cm]
%

Method & Description \\
\cmidrule(r){2-2}
\code{as.list} & return a named
integer vector with the values of the enum and their names.\\
\code{as.character} & character representation of a descriptor\\
\code{toString} & character
representation of a descriptor (same as \code{as.character}) \\
\code{asMessage} & return EnumDescriptorProto message. \\
\code{name} & Return the name of the enum descriptor.\\
\code{fileDescriptor} & Return the fileDescriptor where this field is defined.\\
\code{containing\_type} & Return the containing descriptor of this field.\\
\code{length} & Return the number of constants in this enum.\\
\code{has} & Return TRUE if this enum contains the specified named constant string.\\
\code{value\_count} & Return the number of constants in this enum (same as \code{length}).\\
\code{value} & Return the EnumValueDescriptor of an enum value of specified index, name, or number.\\
\bottomrule
\end{tabular}
\end{small}
\caption{\label{enumdescriptor-methods-table}Description of slots and methods
  for the \code{EnumDescriptor} S4 class.} 
\end{table}

@@

The class \emph{EnumValueDescriptor} represents enumeration value
descriptors in \proglang{R}.  This is a wrapper S4 class around the
\code{google::protobuf::EnumValueDescriptor} \proglang{C++} class.
Table~\ref{EnumValueDescriptor-methods-table} describes the methods
defined for the \code{EnumValueDescriptor} class.

@@

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & External pointer to the \code{EnumValueDescriptor} \proglang{C++} variable \\
\code{name} & simple name of the enum value \\
\code{full\_name} & fully qualified name of the enum value \\[.3cm]
%

Method & Description \\
\cmidrule(r){2-2}
\code{number} & return the number of this EnumValueDescriptor. \\
\code{name} & Return the name of the enum value descriptor.\\
\code{enum\_type} & return the EnumDescriptor type of this EnumValueDescriptor. \\
\code{as.character} & character representation of a descriptor. \\
\code{toString} & character representation of a descriptor (same as \code{as.character}). \\
\code{asMessage} & return EnumValueDescriptorProto message. \\
\bottomrule
\end{tabular}
\end{small}
\caption{\label{EnumValueDescriptor-methods-table}Description of slots
  and methods for the \code{EnumValueDescriptor} S4 class.}
\end{table}

@@

\begin{table}[tbp]
\centering
\begin{small}
\begin{tabular}{lp{10cm}}
\toprule
Slot & Description \\
\cmidrule(r){2-2}
\code{pointer} & external pointer to the \code{FileDescriptor} object of the \proglang{C++} proto library. Documentation for the
\code{FileDescriptor} class is available from the Protocol Buffer project page:
\url{http://developers.google.com/protocol-buffers/docs/reference/cpp/google.protobuf.descriptor.html#FileDescriptor} \\
\code{filename} & fully qualified pathname of the \code{.proto} file.\\
\code{package} & package name defined in this \code{.proto} file.\\[.3cm]

Method & Description \\
\cmidrule(r){2-2}
\code{name} & Return the filename for this FileDescriptorProto.\\
\code{package} & Return the file-level package name specified in this FileDescriptorProto.\\
\code{as.character} & character representation of a descriptor. \\
\code{toString} & character representation of a descriptor (same as \code{as.character}). \\
\code{asMessage} & return FileDescriptorProto message. \\
\code{as.list} & return named list of descriptors defined in this file descriptor.\\
\bottomrule
\end{tabular}
\end{small}
\caption{\label{filedescriptor-methods-table}Description of slots and methods for the \code{FileDescriptor} S4 class.}
\end{table}

The class \emph{FileDescriptor} represents file descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::FileDescriptor} \proglang{C++} class.
Table~\ref{filedescriptor-methods-table} describes the methods
defined for the \code{FileDescriptor} class.

>>>>

Table~\ref{class-summary-table} lists the six primary Message and
Descriptor classes in \pkg{RProtoBuf}.
Please see the package
documentation for a complete description of the slots and methods for
each class.

% [bp]
\begin{table}
\centering
\begin{tabular}{lccl}
\toprule
Class               & Slots & Methods & Dynamic dispatch\\
\cmidrule{2-4}
Message             & 2 & 20 & yes (field names)\\
Descriptor          & 2 & 16 & yes (field names, enum types, nested types)\\
FieldDescriptor     & 4 & 18 & no\\
EnumDescriptor      & 4 & 11 & yes (enum constant names)\\
EnumValueDescriptor & 3 & \phantom{1}6 & no\\
FileDescriptor      & 3 & \phantom{1}6 & yes (message/field definitions)\\
\bottomrule
\end{tabular}
\caption{\label{class-summary-table}Overview of class, slot, method and
  dispatch relationships.}
\end{table}

@@

The \code{Message} S4 class represents Protocol Buffer Messages and
is the core abstraction of \pkg{RProtoBuf}. Each \code{Message}
contains a pointer to a \code{Descriptor} which defines the schema
of the data defined in the Message, as well as a number of
\code{FieldDescriptors} for the individual fields of the message.

@@

@@

@@

The class \emph{FieldDescriptor} represents field
descriptors in \proglang{R}. This is a wrapper S4 class around the
\code{google::protobuf::FieldDescriptor} \proglang{C++} class.

<<>>=
tutorial.Person$email
tutorial.Person$email$is_required()
tutorial.Person$email$type()
tutorial.Person$email$as.character()
@

@@

The class \emph{EnumDescriptor} represents enum descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::EnumDescriptor} \proglang{C++} class.

@@

@@

The class \emph{EnumValueDescriptor} represents enumeration value
descriptors in \proglang{R}.  This is a wrapper S4 class around the
\code{google::protobuf::EnumValueDescriptor} \proglang{C++} class.

@@

@@

The class \emph{FileDescriptor} represents file descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::FileDescriptor} \proglang{C++} class.
